There once was a grid at ol' Carkeek

### 2016-03-18 Manuscript/carkeek_grid.tex
add to manuscript

%-----------------------------------METHODS-------------------------------------
\section*{Methods}
\subsection*{Environmental Sampling}
We collected samples from 8 points along three parallel transects, separated by 1000m.
The first sample was collected over a lower-intertidal patch of \textit{Zostera marina}, with samples taken at 75, 125, 250, 500, 1000, 2000, and 4000 meters along the transect.

\subsection*{Laboratory Methods}
The sequencing run consisted of 14 samples ('libraries') prepared using different index sequences ligated during library preparation.
Of these libraries, ten comprised of amplicons prepared using the 16S protocol reported above, and four comprised of amplicons prepared using a 12S protocol similar to that reported by (CITE PORT 2015).

@@

\subsection*{Model Formulation}
We use the general framework outlined by Shelton et al (CITE).
That study outlined the structure for estimation of the proportional biomass of a taxon ($B_i$) given the proportional counts of sequences recovered from a parallel sequencing run ($Z_i$).

@@

%-----------------------------------RESULTS-------------------------------------
\section*{Results}
We found that if you have two apples, and someone gives you another two apples, you have four apples.

>>>>

%-----------------------------------METHODS-------------------------------------
\section*{Methods}
\subsection*{Environmental Sampling}
We collected samples from 8 points along three parallel transects separated by 1000 meters.
The first sample was collected over a lower-intertidal patch of \textit{Zostera marina}, with samples taken at 75, 125, 250, 500, 1000, 2000, and 4000 meters along the transect.

\subsection*{Laboratory Methods}

Samples were randomly assigned to PCR primer and library adapter index sequences. 
The sequencing run consisted of 14 samples ('libraries') prepared using different index sequences ligated during library preparation.
Of these libraries, ten comprised of amplicons prepared using the 16S protocol reported above, and four comprised of amplicons prepared using a 12S protocol similar to that reported by (CITE PORT 2015).

@@

% Calculate Moran's I on ?(relative abundance | raw count) of ?(taxa | OTU | uniq_sequences) to report dispersion of DNA in space?

\subsection*{Spatial Model Formulation}
We use the general framework outlined by Shelton et al (CITE).
That study outlined the structure for estimation of the proportional biomass of a taxon ($B_i$) given the proportional counts of sequences recovered from a parallel sequencing run ($Z_i$).

@@

%-----------------------------------RESULTS-------------------------------------
\section*{Results}
\subsection*{Data Quality (Bioinformatics)}
All value ranges are reported as (mean $\pm$ standard deviation).\\
There was a very low frequency of cross-contamination from other libraries into those reported here (5e-05$\pm$8e-05; max 0.00034)

\subsection*{Community Analysis}

\subsection*{Spatial Model Output}
